---
title: "P8130_hw3_wl2829"
author: "Wentong"
date: "10/15/2021"
output: pdf_document
---
## Problem 1

Read the dataset and save the sample.
```{r}
population = read.csv("./ce8130entire.csv")
library(dplyr)
set.seed(1000) 
A = population %>%
  group_by(sex) %>%
  sample_n(100)
```

## Problem 2

Save a separate sample.
```{r}
set.seed(1000) 
B = population %>%
  group_by(sex) %>%
  sample_n(30)
```

## Problem 3
Display the distribution of CE cost in $USD separately for men and women using side-by-side boxplots and histograms.

Side-by-side box plots
```{r}
boxplot(A$totchg ~ A$sex, names=c("Men","Women"), ylab ="EC cost in $USD", xlab ="Sex")
```

Histograms
```{r}
library(ggplot2)
A %>% 
  mutate(sex = recode(sex, `1` = "Man", `2` = "Woman")) %>% 
  ggplot(aes(x = totchg, fill = sex)) +
  geom_histogram(position = "identity", bins = 30, alpha = 0.4)
```

## Problem 4

Calculate the mean CE cost and 95% confidence interval separately for men and women in sample “A” as
well as sample “B”.
```{r}
A$sample = "Sample A"
B$sample = "Sample B"
A_B = rbind(A, B)

library(Rmisc)

A_B_summary <- summarySE(A_B, measurevar="totchg", groupvars=c("sex","sample"))
A_B_summary$sex <- as.factor(A_B_summary$sex)
p_dodge = position_dodge(0.1) # move them .05 to the left and right
plot = ggplot(A_B_summary, aes(x=sample, y=totchg, colour=sex)) +
geom_errorbar(aes(ymin=totchg-ci, ymax=totchg+ci), width=.1, position=p_dodge) +
geom_point(position=p_dodge)

plot
```
The confidence interval of B is wider especially man, considering it has a smaller sample.

## Problem 5
Conduct test of equality of variance of CE cost among men vs women in sample A
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r}
var.test(totchg ~ sex, data = A)
```
p-value = 0.2797 > 0.05
We cannot reject the null hypothesis at significance level 0.05. Thus, two samples have equal variance.

## Problem 6
Using sample “A”, calculate the difference between the mean CE costs for men and women.
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
```{r}
A_men = 
  A %>% 
  filter(sex == 1)

A_women = 
  A %>% 
  filter(sex == 2)

t.test(A_men$totchg, A_women$totchg, alternative = "two.sided", var.equal = TRUE)
```
The difference between the means is 
7449.33 - 6941.84 = 507.49
The 95% confidence interval is 
(-2322.547, 1307.567)

## Problem 7
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

```{r}
res <- t.test(totchg ~ sex, data = A, var.equal = TRUE)
res
```

## Problem 8




## Problem 9
```{r}
population_man = 
  population %>% 
  filter(sex == 1)

population_woman = 
  population %>% 
  filter(sex == 2)
man_mean = mean(population_man$totchg)
woman_mean = mean(population_woman$totchg)
mean_dif = man_mean - woman_mean
```
The mean for men is `r man_mean` and for women is `r woman_mean`. The difference is `r mean_dif`.

## Problem 10

This question could be regarded as a binomial distribution. The number of the intervals which contain true mean difference is equal to the expectation of the binomial distribution. 
E = np = 140 x 0.95 = 133
About 133 students' intervals contain the true population mean difference.

```{r}
p140 = dbinom(140, size=140, prob=0.95)
```

the probability that all 140 will contain the true population mean difference is `r p140`
